GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-27 paper/kbanotebook2013/content/implementation.tex

\section{Implementation}

We extract aliases for entities from Wikipedia automatically both using API 
and using the actual page content, then apply pattern matching rules for slot 
value extraction.

@@

We use Wikipedia API to get some aliases automatically. This is done by 
retrieving backlink references (redirects of a wiki entity). Unfortunately 
this is not good enough and to enhance recall we need more aliases. To have 
better use of a wiki page we parse HTML DOM of the page, then use regular 
expressions to extract the bold phrases of the first paragraph as alias of the 
actual entity. Based on our observation this is a very accurate heuristic and 
provides us with lots of famous aliases of the entities. To consider other 
typical cases we consider some generic first name last name order swapping 
conventions such as Bill Gates -\textgreater Gates, Bill.

\subsection{Pattern Matching}

In this system, we use pattern matching methods to find corresponding slot 
values for entities. The procedure is: 1) Find stream items that contain the 
entities by using alias names of the entities. 2) Inside these stream items, 
fetch the sentences which contain entities by using alias names and the 
coreference information provided by Lingpipe tags. 3) Use these sentences to 
match existing patterns. 4) When patterns matched, generate SSF results.

@@

Here is an example for the second type: \textless PER, AwardsWon, awarded, 
right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the “awarded” since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

Another example for the third type: \textless PER, DateOfDeath, died, right, 
last night\textgreater. In this pattern, “last night” means we are looking for 
exactly the phrase “last night” to the right of “died”. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like “last night” as a DATE entity.

@@

For accuracy, we have found that there are three major kinds of errors: 1) 
wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
by the patterns. We solve the first problem by using the wikipedia or twitter 
information of the entities to get better alias names. And we use
post- processing to reduce the second and third types of errors.

\subsection{Post Processing}

@@

The output contains many duplicate entries. As we read the list of extrated 
slots we create rules to define "duplicate". Duplicates can be present in a 
window of rows; we use a window size of 2 meaning we only be adjacent rows. 
Two rows are duplicates if 1) they have the same exact extraction, 2) if the 
rows have the same slot name and a similar slot value and 3) if the extracted 
sentence for a particular slot types come from the same sentence.

 New slots can be deduced from existing slots by defineing inference rules. 
 For example, two slots for the task are "FounderOf" and "FoundedBy". A safe 
 assumtion is these slot names are biconditional logical connectives with the 
 entities and slot values. Therefore, we can express a rule "X FounderOf Y" 
 equals "Y FoundedBy X" where X and Y are single unique entities. Additionally,
 we found that the slot names "Contact\_Meet\_PlaceTime" could be infered as
 "Contact\_Meet\_Entity" if the Entity was a FAC and the extracted sentence 
 contained an additional ORG/FAC tag.  
We also remove erronious slots that have extractions that are several pages in 
length or tool small. Errors of extracting long sentences can typically be 
attributed to poor sentence parsing of web documents. We have some valid
"small" extractions. For example a comma may separate a name and a title
(e.g. "John, Professor at MIT"). But such extraction rules can be particularly 
noisy, so we check to see if the extracted values have good entity values.

@@

\subsection{Shortcomings}

The missing twitter entities are more than the 50\% of the twitter entities we 
need to work on and this is a very very bad performance. One reason could be 
that those entities are not very famous. For example Brenda Weiler google 
search result is 860,000 documents our of billions of web documents. For our 
small portion of the web it might make sense. If you pay attention to the 
histogram of the entities found you'll note that more than half of the 
entities have appeared in less than 10 StreamItems. A good portion have 
appeared only once. Which the document does not necessarily have good 
information for us.

A theory is that we are falling behind because we are using the cleansed 
version of the corpus. We believe there has been a reason that TREC has 
included the actual HTML document as well as the cleansed version. This 
definitely will convey some information to us. If it was as easy as reading 
some clean text they wouldn't bother including so much data for teams to be 
useless. So we guess is that we are missing some information from not using 
the actual document. And, we are looking for tokens with entity value set 
which will depend us dramatically on the accuracy of lingpipe, which is a fast 
algorithm but is not as good as other NLP tools can be e.g. Stanford NLP.

>>>>

\section{Implementation}
\label{section:implementation}

Our contribution is that we perform pattern matching that conforms to each slot 
value along with post-processings to eliminate noisy outputs. We extract aliases for entities from Wikipedia automatically both using API 
and using the actual page content, then apply pattern matching rules for slot 
value extraction.

%\ceg{Instead of this paragraph we talk about what this %section will
%contain. We can discuss the input/output of the system %too.
%}

@@

We use Wikipedia API to get some aliases automatically. This is done by 
retrieving backlink references (redirects of a wiki entity). Unfortunately 
this is not good enough and to enhance recall we need more aliases. To have 
better use of a wiki page we parse HTML DOM of the page, then use regular 
expressions to extract the bold phrases of the first paragraph as alias of the 
actual entity. Based on our observation this is a very accurate heuristic and 
provides us with lots of famous aliases of the entities. To consider other 
typical cases we consider some generic first name last name order swapping 
conventions such as Bill Gates $\rightarrow$ Gates, Bill.

\subsection{Streaming Slot Value Extraction}

In this system, we use pattern matching methods to find corresponding slot 
values for entities. This is done by observing the training data which is the first four months of the corpus(Oct 2011 - Feb 2012). The procedure is: 1) Find stream items that contain the 
entities by using alias names of the entities. 2) Inside these stream items, 
fetch the sentences which contain entities by using alias names and the 
coreference information provided by Lingpipe tags. 3) Use these sentences to 
match existing patterns. 4) When patterns matched, generate SSF results.

@@

Here is an example for the second type: \textless PER, AwardsWon, awarded, 
right, NP\textgreater, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the “awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

Another example for the third type: \textless PER, DateOfDeath, died, right, 
last night\textgreater. In this pattern, “last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.

@@

For accuracy, we have found that there are three major kinds of errors: 1) 
wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched 
by the patterns. We solve the first problem by using the Wikipedia or twitter 
information of the entities to get better alias names. And we use
post- processing to reduce the second and third types of errors.

\subsection{High Accuracy Filter}

@@

The output contains many duplicate entries. As we read the list of extracted 
slots we create rules to define ``duplicate''. Duplicates can be present in a 
window of rows; we use a window size of 2 meaning we only be adjacent rows. 
Two rows are duplicates if they have the same exact extraction, or if the 
rows have the same slot name and a similar slot value or if the extracted 
sentence for a particular slot types come from the same sentence.

 New slots can be deduced from existing slots by defining inference rules. 
 For example, two slots for the task are ``FounderOf'' and ``FoundedBy''. A safe 
 assumption is these slot names are biconditional logical connectives with the 
 entities and slot values. Therefore, we can express a rule ``X FounderOf Y'' 
 equals ``Y FoundedBy X'' where X and Y are single unique entities. Additionally,
 we found that the slot names ``Contact\_Meet\_PlaceTime'' could be inferred as
 ``Contact\_Meet\_Entity'' if the Entity was a FAC and the extracted sentence 
 contained an additional ORG/FAC tag.  
We also remove erronious slots that have extractions that are several pages in 
length or tool small. Errors of extracting long sentences can typically be 
attributed to poor sentence parsing of web documents. We have some valid
``small'' extractions. For example a comma may separate a name and a title
(e.g. ``John, Professor at MIT''). But such extraction rules can be particularly 
noisy, so we check to see if the extracted values have good entity values.

@@

### 2013-09-27 paper/kbanotebook2013/content/introduction.tex

In this article we will describe the approach the GatorDSR team from the 
University of Florida in addressing the challenge at NIST’s Text 
REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013 
In the first section we describe 
the system design and articulate its evolution during the whole process, 
challenges and needs that we have overcome. In the second section we will go 
through the details of the NLP techniques we took at streaming slot filling
(SSF): given a slot name (entity + relation type) we fill in the slot value
(relation value) on structured text documents.

\ceg{Add a discussion of why machine driven kb population is important.}
The task is that given certain Wikipedia or Twitter entities 
(wiki/twitter URLs) and certain relations of interest given in Table 1, 
extract as many triple relations as possible (hence, slot filling). This can 
be used to automatically populate knowledgebases such as free-base or DBPedia 
or even filling in the information boxes at Wikipedia. The corpus is in 
English and is a snapshot of part of the web containing arXiv, social, news, 
linking, weblog, forum, classifieds, reviews, and memetracker documents. Each 
document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields.

Since this is \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus, which 
ranges from October 2011 to February 2013. Below you can view the slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}

\begin{table}[b]
\caption{Ontology of Slot Name Categories }
\centering

\begin{tabular}{|c|c|c|}
\hline 
PER & FAC & ORG \\ 
\hline 
\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
DateOfDeath \\ 
CauseOfDeath\\
Titles\\
FounderOf\\
EmployeeOf\end{tabular}
  &
   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
   & 
   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
\hline 
\end{tabular} 
\end{table}

Example 1: "Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
at Elysian Charter School, were honored Friday morning by C-SPAN and received 
\$1,500 as well as an iPod Touch after winning a nationwide video contest."

@@

Affiliate:  "Matthew DeLorenzo"
Affiliate:  "Josiah Vega"

NOT an affiliate:  "C-SPAN"
NOT an affiliate:  "iPod Touch"

Example 2: "Veteran songwriters and performers Ben Mason, Jeff Severson and 
Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
at ArtSpace, 410 S. Maple Avenue."

@@

Affiliate: "Ben Mason"
Affiliate: "Jeff Severson"
Affiliate: "Jeff Smith"

NOT an Affiliate: "Creative Caldron"
NOT an Affiliate: "Art Space"

Example 3:  "Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
district judge and former state attorney general, unveiled the crest Friday 
during a ceremony at the North Dakota Capitol."

@@

Contact\_Meet\_PlaceTime: "Friday during a ceremony at the North Dakota Capitol"

In our approach we will perform pattern matching that conforms to each slot 
value along with post-processings to eliminate noisy outputs.

\ceg{How will each submission be evaluated?}

>>>>

One of the important challenges in maintaining the most popular free, web-based, collaborative, multilingual encyclopedia in the internet (Wikipedia) is to make sure its descriptions are upto date. It has been observed that there is a considerable time lag between the publication date of cited news articles and the date of an edit to Wikipedia (WP) creating the citation. In a case-study, the time lag for a sample of \~60,000 web pages cited by WP articles in the Living\_people category, The median time is over a year and the distribution has a long and heavy tail\cite{JFrank12}. It is also noted that the majority of wikipedia entities have updates on their WP article much less frequently than their mention frequency.

Such stale entries are the norm in any large knowledge base (KB), because the number of humans maintaining the knowledge base is far fewer than the number of entities in the KB. Further, the number of mentions is much larger than the number of entities. This mismatch between human maintainers and the large stream of mentions to entities of interest is effectively a definition of a ``large'' KB \cite{JFrank12}. So, knowledge-bases are important and we are working on accelerating populating them.

In this article we will describe the approach the GatorDSR team from the 
University of Florida in addressing the challenge at NIST’s Text 
REtrieval Conference (TREC) --- Knowledge Base Acceleration track 2013 
In the first section we describe 
the system design and articulate its evolution during the whole process, 
challenges and needs that we have overcome. In the second section we will go 
through the details of the NLP techniques we took at streaming slot filling
(SSF): given a slot name (entity + relation type) we fill in the slot value
(relation value) on structured text documents. For similar approaches regarding last year's track you can refer to \cite{ji2011knowledge}.

%\ceg{Add a discussion of why machine driven kb population is important.}
The task is that given certain Wikipedia or Twitter entities 
(wiki/twitter URLs) and certain relations of interest given in Table  \ref{table:slotNameOntology}, extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia 
or even filling in the information boxes at Wikipedia. The corpus is in 
English and is a snapshot of part of the web containing document types described in Table \ref{table:documentsDist}. Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
To have a sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields.

Since this is \textit{streaming} slot filling, we are only interested in new 
slot values that were not substantiated earlier in the stream corpus, which 
ranges from October 2011 to February 2013. Below you can view some slot values 
and their types, the comprehensive description of which can be found at
\cite{tackbp} and \cite{aec}. These examples demonstrate that out of an ordinary sentence in the general web, which parts are of interest for us and which should be avoided to be returned as slot values of a given entity. You can view that sometimes it can get fairly complex, so a good extraction scheme is essential. The evaluation metric is that the extractions will be submitted to KBA assessors and they will determine the overall performance for comparison.

Assessors were instructed to ``use the wikipedia article to identify (disambiguate) the entity, and then imagine forgetting all info in the WP article and asking whether the text provides any information about the entity''\cite{JFrank12}. Documents would be devided according to two metrics: 1) mentioning the entity or not, 2) relevance level to the entity:
\begin{itemize}
\item \textbf{Mention} 
\begin{itemize}
\item \textbf{Mention:} Document explicitly mentions target entity, such as full name, partial name, nickname, pseudonym, title, stage name.
\item \textbf{Zero-mention:} Document does not directly mention target. Could still be relevant, e.g. metonymic references like ``this administration'' -- \textgreater ``Obama''. See also synecdoche. A document could also be relevant to target entity through relation to entities mentioned in document -- apply this test question: can I learn something from this document about target entity using whatever other information I have about entity?
\end{itemize}
\item \textbf{Relevance}
\begin{itemize}
\item \textbf{Garbage:} not relevant, e.g. spam.
\item \textbf{Neutral:} Not relevant, i.e. no info could be deduced about entity, e.g., entity name used in product name, or only pertains to community of target such that no information could be learned about entity, although you can see how an automatic algorithm might have thought it was relevant.
\item \textbf{Relevant:} Relates indirectly, e.g., tangential with substantive implications, or topics or events of likely
impact on entity.
\item \textbf{Central:} Relates directly to target such that you would cite it in the WP article for this entity, e.g. entity is a
central figure in topics/events.

\end{itemize}
\end{itemize}

The details of the metric for SSF will favor systems that most closely match the changes in the ground truth time line of slot values. This is done by searching for other documents that mentioned an entity and exactly matched the slot fill strings selected by the assessors.

\begin{table}[b]
\caption{Ontology of Slot Name Categories }
\centering
\label{table:slotNameOntology}

\begin{tabular}{|c|c|c|}
\hline 
\textbf{PER} & \textbf{FAC} & \textbf{ORG} \\ 
\hline 
\begin{tabular}{@{}l@{}}Affiliate \\ AssociateOf \\ Contact\_Meet\_PlaceTime \\ AwardsWon \\ 
DateOfDeath \\ 
CauseOfDeath\\
Titles\\
FounderOf\\
EmployeeOf\end{tabular}
  &
   \begin{tabular}[b]{l}Affiliate \\ Contact\_Meet\_Entity \end{tabular} 
   & 
   \begin{tabular}{@{}l@{}}Affiliate \\ TopMembers \\ FoundedBy\end{tabular} \\ 
\hline 
\end{tabular} 
\end{table}

\begin{table}[b]
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

\begin{tabular}{|c|l|}
\hline 
\textbf{\# of Documents} & \textbf{Document Type}\\ 
\hline 
10988 & 	arxiv (full text, abstracts in StreamItem.other\_content) \\ \hline
34887 & CLASSIFIED (spinn3r)  \\ \hline
77674 & FORUM (spinn3r)  \\ \hline
12947 & linking (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
141936 & MAINSTREAM\_NEWS (spinn3r)  \\ \hline
4137 & MEMETRACKER (spinn3r)  \\ \hline
280629 & news (reprocessed from kba-stream-corpus-2012, same stream\_id)  \\ \hline
6347 &  REVIEW (spinn3r) \\ \hline
688848 & 	 social (reprocessed from kba-stream-corpus-2012 plus extension, same stream\_id)  \\ \hline
740987 & WEBLOG (spinn3r)  \\ \hline

\hline 
\end{tabular} 
\end{table}

\noindent Example 1: ``Matthew DeLorenzo and Josiah Vega, both 14 years old and students 
at Elysian Charter School, were honored Friday morning by C-SPAN and received 
\$1,500 as well as an iPod Touch after winning a nationwide video contest.''

@@

Affiliate:  ``Matthew DeLorenzo''
Affiliate:  ``Josiah Vega''

NOT an affiliate:  ``C-SPAN''
NOT an affiliate:  ``iPod Touch''

\noindent Example 2: ``Veteran songwriters and performers Ben Mason, Jeff Severson and 
Jeff Smith will perform on Saturday, April 14 at 7:30 pm at Creative Cauldron 
at ArtSpace, 410 S. Maple Avenue.''

@@

Affiliate: ``Ben Mason''
Affiliate: ``Jeff Severson''
Affiliate: ``Jeff Smith''

NOT an Affiliate: ``Creative Caldron''
NOT an Affiliate: ``Art Space''

\noindent Example 3:  ``Lt. Gov. Drew Wrigley and Robert Wefald, a retired North Dakota 
district judge and former state attorney general, unveiled the crest Friday 
during a ceremony at the North Dakota Capitol.''

@@

Contact\_Meet\_PlaceTime: ``Friday during a ceremony at the North Dakota Capitol''

%\ceg{How will each submission be evaluated?}

### 2013-09-27 paper/kbanotebook2013/content/system.tex

\begin{figure}[b]
\centering
\includegraphics[width=4.5in]{./images/system.eps}
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

\section{Pipeline}

In this section we provide a high level description of the pipeline(system) 
design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) 
task. Our pipeline of processing the corpus consists of a two layer indexing 
system main section in our system regarding indexing the corpus, We started 
off by trying to use the off-the-shelf tools for this task. Mainly we started 
by using Scala/Spark\cite{ferc11} to benefit from the parallelization 
performance there.  Spark was not as efficient as expected and the overhead 
was much more than tolerable. We tried to use Scala parallelization itself to 
do the job, and unfortunately it did not satisfy our needs, there was 
excessive memory overhead on map reduce jobs. We migrated the core of the 
system to Java Parallelism APIs and that was not good enough either, we wanted 
better. So we built our own parallel system which in actual performance had 
the least of overhead, the least memory consumption and the most robust memory 
model which avoided unpredictable CPU stalls on garbage collections in 
processing the corpus. In what follows we will describe each step of this 
evolution in details. Figure~\ref{fig:system} shows a schematic view of the 
system. The platform that we run our pipeline over was a 32 core server having 
64GB of memory.

@@

Regarding Cumulative Citation Recommendation we perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable.
For future iterations of the paper we have ideas on how to score documents 
based on their likelihood of citation worthiness but for this iterations we 
treat all mentioning documents equally likely. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have highly low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents. Regarding mentioning but 
garbage, neutral or central documents we produce more slot values which can be 
later on filtered out in the high accuracy filter section.

\subsection{Streaming Slot Filling}

Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

@@

The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules.

>>>>

\begin{figure}
\centering
%\includegraphics[width=4.5in]{./images/system.eps}
\includegraphics[width=6in]{./images/SystemBW.eps}
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

\section{System Architecture}

As shown in Figure \ref{fig:system}, our system is built in a pipeline manner which gives it the advantage to run each section separately and allow stream processing without wasting resources being clogged by one operation while others are waiting. Below, we describe each component briefly and in Section \ref{section:implementation} we will go through technical details.

%\ceg{Discuss current system first. If you want to keep the decisions points that led to the current architecture, make it a subsection.}

\subsection{Preprocessing}

To begin, we need to have real world aliases of entities. TREC KBA prohibits Wikipedia entities to have any manual aliases being added and only allows automatic ways. We use Wikipedia API backlink references (redirects to a wiki entity) as aliases of the entity. We also use some techniques to extract some aliases from within the text of a wiki entity, which will be described later on. This whole process is referred to as \textbf{Alias Extraction (Wiki API, Wiki text)} Regarding Twitter entities this limit is lifted and participants are allowed to manually add aliases for them. Part of the reason is that Twitter environment is composed of so much informal and dialectic language which makes it extremely difficult to extract context out of tweets or entities descriptions in their profiles. This process of extracting aliases for Twitter entities is referred to as \textbf{Manual Alias Extraction (Twitter)}.

Once aliases are available we pass them through some rules of generating proper name orders which will produce various instances of writing a name. As a basic example Bill Gates can be written as Gates, Bill. This will allow the system to capture various notation forms of aliases. This part of the system is referred to as \textbf{Name Order Generator}.

The main goal of Cumulative Citation Recommendation is to have an aggregate list of documents that are worthy of being cited in a Wikipedia page. Regarding Cumulative Citation Recommendation we perform exact string matching 
and treat all the documents that mention an entity equally likely to be citable.
For future iterations of the paper we have ideas on how to score documents 
based on their likelihood of citation worthiness but for this iterations we 
treat all mentioning documents equally likely. One of the reasons for this is 
that in former TREC KBA reports \cite{JFrank12} there were observations of how 
non-mentioning documents have highly low chance of being citable in Wikipedia.
So we take on that and ignore non-citing documents. Regarding mentioning but 
garbage, neutral or central documents we produce more slot values which can be 
later on filtered out in the high accuracy filter section.

Our pipeline of processing the corpus consists of a two layer indexing system referred to as \textbf{Chunk Files Index Generator} and \textbf{StreamItems Index Generator}.  Chunk Files Index Generator will generate indexes of the chunk files that contain a mention of any of the desired entities. StreamItems Index Generator on the other hand will index StreamItems that contain a mention of a given entity respectively. This two level indexing will eliminate the need to process each and every ChunkFile/StreamItem for every entity.

@@

%\ceg{This section should be structured as follows:
%1: Introduce CCR (Motivation, Expectations)
%2: Our high level approach
%3: Discussion of our design (Like already discussed)
%}

\subsection{Streaming Slot Filling}
%\ceg{See the previous note.}
As described in the Introduction, the general purpose of slot filling is to extract proper values for relations of interest, some of which can be found in Table \ref{table:slotNameOntology}. This is called Stream Slot Filling due to the fact that it is assumed that data is being generated as time goes on and for each extraction we should only consider current or past data. In our schematic diagram we refer to this as \textbf{Streaming Slot Value Extraction}. Stream slot filling is done by pattern matching documents with manually 
produced patterns for slots of interest. The way we do this is by observing a 
sentence that has a mention of the entity or one of its coreferences. An 
anchor word in the sentence related to the slot name is located and we match 
either left or right of the anchor word for potential slot values.

@@

The SSF output of many extractions is noisy. The data contains duplicates and 
incorrect extractions. We can define rules to sanitize the output only using 
the information present in the SSF file. The file is processed in time order, 
in a tuple-at-a-time fashion to minimize the impact on accuracy. We define 
two classes of rules deduplication rules and inference rules. In our diagram we refer to this component as \textbf{High Accuracy Filter}.
